03 - PubliliaFitness - Modeling offspring surivorship

### 2023-08-26 scripts/Publilia-03-survivorship.Rmd
minor edits to ensure scripts 01-03 run after overhaul of strats_data
moving custom functions to separate files for each script

---
title: "Publilia-03-survivorship.Rmd"
author: "micah fletcher"
date: "8/4/2023"
output: html_document
---

@@

source(here("R/custom_functions.R"))
```

>>>>

---
title: '03 - PubliliaFitness - Modeling offspring surivorship'
author: "Micah Fletcher"
date: '`r Sys.Date()`'
output: 
  rmdformats::robobook:
  fig_width: 9
toc_depth: 3
---

@@

source(here("R/utils.R"))
source(here("R/Publilia-03-survivorship-functions.R"))
```
